---
title: "Attempt to documentation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Attempt to documentation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}



knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
  
)
```

```{r setup}
library(Documentation)
```
## Explanatory Notes

This slim package consists of a compilation of functions that help the user to implement basic jobs with data provided from the US National Highway Traffic Safety Administration's 
Fatality Analysis Reporting System. A sample of the data is integrated with package to serve as a testing ground and appropriate documentation is present for both the functions and the data types, which can be accessed in the usual syntax form: `?"name of data or function"`.

### Data

- accident_2013.csv.bz2
- accident_2014.csv.bz2
- accident_2015.csv.bz2
```{r data_exposure}





```


The data are in .csv format, compressed and can be read in with the function `fars_read` which accepts the appropriate filename in quotes, i.e.

  










